\mireval{}

### 2014-05-08 paper/paper.tex
Shortening melody section and changing content to match other sections

\subsection{Melody Extraction}
\subsubsection{Task definition}
Melody extraction algorithms aim to produce a sequence of frequency values
corresponding to the pitch of the dominant melody from a musical recording
\cite{salamon:MelodyReview:IEEESPM13}. The estimated pitch is represented as a
time series of fundamental frequency ($f_0$) values in Hz sampled on a fixed
time grid (e.g.~every 10 ms). To evaluate the estimated sequence, a reference
sequence is generated by running a pitch tracker on the monophonic melody track
(requiring access to the multi-track recording session) and manually correcting
any mistakes made by the pitch tracker. The estimate is then evaluated against
the reference by comparing the two frequency sequences on a frame-by-frame
basis, and computing five global measures, first used in the MIREX 2005 AME
evaluation \cite{polinerMelodyEval}. The goal of these measures, defined below,
is to assess the algorithm's performance on two subtasks of melody extraction:
(1) pitch estimation, i.e.~how well the algorithm estimates the pitch of the
melody, and (2) voicing detection, i.e.~how well the algorithm determines when
the melody is present in a frame (a \textit{voiced} frame) or absent (an
\textit{unvoiced} frame). To allow evaluation of these two subtasks
independently, a melody extraction algorithm can provide a frequency estimate
even for frames it has determined to be unvoiced.

\subsubsection{Evaluation measures}
The following definitions are taken from
\cite{salamon:MelodyReview:IEEESPM13} with permission from the authors. Let the estimated melody pitch frequency
vector be $\mathbf{f}$, and the true sequence (reference) be $\mathbf{f}^*$. Let
us also define a voicing indicator vector $\mathbf{v}$, whose $\tau^\text{th}$
element $v_\tau = 1$ when a melody pitch is detected, with corresponding ground
truth $\mathbf{v}^*$.  We also define an ``unvoicing'' indicator $\bar{v}_\tau =
1 - v_\tau$.  Recall that an algorithm may report an estimated melody pitch
($f_\tau > 0$) even for times where it reports no voicing ($v_\tau = 0$).   
Then the measures are:
\begin{itemize}
  \item \textbf{Voicing Recall Rate}: The proportion of frames labeled as
  melody frames in the reference that are estimated as melody frames by the
  algorithm.
\begin{equation}
\text{Rec}_\text{vx} = \frac{\sum_\tau v_\tau v^*_\tau}{\sum_\tau v^*_\tau}
\end{equation}

  \item \textbf{Voicing False Alarm Rate}: The proportion of frames
  labeled as non-melody in the reference that are mistakenly estimated as
  melody frames by the algorithm.
\begin{equation}
\text{FA}_\text{vx} = \frac{\sum_\tau v_\tau \bar{v}^*_\tau}{\sum_\tau \bar{v}^*_\tau}
\end{equation}

  \item \textbf{Raw Pitch Accuracy}: The proportion of melody frames in the
  reference for which $f_\tau$ is considered
  correct (i.e.~within half a semitone of the ground
  truth $f^*_\tau$).
\begin{equation}
\text{Acc}_\text{pitch}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] }{\sum_\tau v^*_\tau}
\end{equation}
where $\mathcal{T}$ is a threshold function defined by:
\begin{equation}
\mathcal{T}[a] = \begin{cases}
1 \quad \text{if } |a| < 0.5 \\
0 \quad \text{if } |a| \ge 0.5
\end{cases}
\end{equation}
and $\mathcal{M}$ maps a frequency in Hertz to a melodic 
axis as a real-valued number of semitones above an arbitrary
reference frequency $f_\text{ref}$:
\begin{equation}
\mathcal{M}(f) = 12 \log_2\left( \frac{f}{f_\text{ref}} \right)
\end{equation}

  \item \textbf{Raw Chroma Accuracy}: As raw pitch accuracy, except
  that both the estimated and reference $f_0$ sequences are mapped onto a
  single octave. This gives a measure of pitch accuracy which ignores octave
  errors, a common error made by melody extraction systems:
\begin{equation}
\text{Acc}_\text{chroma}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\left<\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau)\right>_{12} \right] }{\sum_\tau v^*_\tau}
\end{equation}
Octave equivalence is achieved by taking the difference between the semitone-scale pitch 
values modulo 12 (one octave), where
\begin{equation}
\left<a\right>_{12} = a - 12 \lfloor \frac{a}{12} + 0.5 \rfloor .
\end{equation}

  \item \textbf{Overall Accuracy}: this measure combines the performance of the
  pitch estimation and voicing detection tasks to give an overall performance
  score for the system. It is defined as the proportion of all frames
   correctly estimated by the algorithm, where for non-melody
  frames this means the algorithm labeled them as non-melody, and for melody
  frames the algorithm both labeled them as melody frames and provided a correct
  $f_0$ estimate for the melody (i.e.~within half a semitone of the
  reference):

\begin{equation}
\text{Acc}_\text{ov} 
= \frac{1}{L} \sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] + \bar{v}^*_\tau \bar{v}_\tau 
\end{equation}
where $L$ is the total number of frames.
\end{itemize}

The performance of an algorithm on an entire music collection for a given
measure is obtained by averaging the per-song scores for that measure over
all songs in the collection.

\subsubsection{Discussion}

In the measure definitions provided above, it is assumed that both the estimate
and reference sequences are sampled using the same time grid (hop size). In
practice, however, this is not always the case, since the time grid of the
reference depends on the hop size used by the pitch tracker that produced
it, and similarly the time grid of the estimate depends on the specific melody
extraction algorithm that produced it. This means that the sequences must be
resampled onto a common time-grid prior to the computation of the measures. For
the MIREX AME task, any sequence (be it reference or estimate) that is not
sampled using a 10 ms hop size is resampled using $0^{th}$-order interpolation,
i.e.~each frequency value in the target sequence is set to its nearest
neighbour (in time) from the source sequence. This kind of interpolation can
potentially have a detrimental effect on the evaluation, depending on the
difference between the source and target time grids. In particular, it can
result in artificially low scores for sequences with rapidly changing pitch
values, such as opera singing with deep vibrato.

For this reason, the melody evaluator in \mireval{} uses $1^{st}$-order (linear)
interpolation by default in order to map the reference and estimate sequences
onto a common time-grid. Assuming the original timestamps of both sequences
correspond to the \textit{center} of each analysis frame (as they should),
using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
returned by \mireval{} are lower-bounded by the MIREX results and are, in our
view, more accurate. By default, the estimate is resampled using the reference's
time grid so that the reference can be used without any modification.
Alternatively, the user can specify a hop size, in which case both
reference and estimate are resampled onto the new time-grid defined by the hop
size.

>>>>

\subsection{Melody Extraction}
Melody extraction algorithms aim to produce a sequence of frequency values corresponding to the pitch of the dominant melody from a musical recording \cite{salamon:MelodyReview:IEEESPM13}.
Melody annotations are represented as time series of fundamental frequency ($f_0$) values in Hz sampled at discrete points (``frames'') in time.
An estimated pitch series is evaluated against a reference by computing the following five measures defined in \cite{salamon:MelodyReview:IEEESPM13}, first used in the MIREX 2005 Automatic Melody Extraction evaluation \cite{polinerMelodyEval}:
\begin{description}
  \item[Voicing Recall Rate:] The proportion of frames labeled as melody frames in the reference that are estimated as melody frames by the algorithm.
  \item[Voicing False Alarm Rate:] The proportion of frames labeled as non-melody in the reference that are mistakenly estimated as melody frames by the algorithm.
  \item[Raw Pitch Accuracy:] The proportion of melody frames in the reference for which the frequency is considered correct (i.e.~within half a semitone of the reference frequency).
  \item[Raw Chroma Accuracy:] As raw pitch accuracy, except that both the estimated and reference $f_0$ sequences are mapped onto a single octave.
  \item[Overall Accuracy:] The proportion of all frames correctly estimated by the algorithm, where for non-melody frames this means the algorithm labeled them as non-melody, and for melody frames the algorithm both labeled them as melody frames and provided a correct $f_0$ estimate for the melody (i.e.~within half a semitone of the reference).
\end{description}
Prior to computing the measure definitions provided above, both the estimate and reference sequences must be sampled on the same timebase.
